\Large{Holier Than Thou? No Partisan Gap in the Consumption\\ of Pornography Online}\footnote{You can download the replication materials from \href{http://github.com/soodoku/adult}{https://github.com/soodoku/adult}}

### 2023-01-04 ms/adult.tex
revise ms

In this paper, we investigate how much pornography Americans consume online. Using passive browsing data from YouGov, we find that there is a sharp skew in the consumption of pornography, with a small set of users consuming a large chunk of pornography. About 68 percent of the respondents abstained from  pornography online during the month long observation period. Of the people who consumed pornography, the median consumer spent about 44 minutes consuming pornography and the 95th percentile consumer spent 337 minutes.

We also use the data to shed light on an age-old debate---whether Democrats consume more pornography than Republicans or vice versa. Both parties claim the higher moral ground. And in surveys both parties think consumption of pornography is abhorrent, plausibly for different reasons. Unlike previous research, which relied on ecological inference, we find that Democrats consume about as much pornography online as Republicans \citep{macinnis2015american, edelman2009markets}. Adjusting for background attributes like age, gender etc., makes little difference.

\section*{Data}\label{sec:data}
We use passively observed browsing data from a YouGov survey to measure the consumption of adult content \citep{data-dataverse}. YouGov maintains a large online panel recruited through a variety of methods. It uses matched sampling to survey respondents: The provider first draws a random sample from a large synthetic representative sampling frame, finds respondents that match the sampled individuals from its panel, and invites them to take a survey. For details and validation, see \citet{rivers2009}. For this particular sample, panelists also provided de-identified access to their web browsing activity via passive metering software installed voluntarily on their computers. The software, called RealityMine, captures visited web URLs independent of the type of browser or browser-specific privacy settings.

The data are from 1,200 respondents and contains a month of data from June, 2022.  We have data on visits to domains, which are about 6 million in total. For each visit, we have information on the domain (e.g., wikipedia.org), the time of visit, and the time spent on the domain. 
We capture about 64k unique sites, of which 900 are pornographic sites (1.4\$ of sites).

Our data also comes with characteristics for the 1,200 individuals. We have data on demographic characterists like birth year, state, gender, race, and education level. We also have information on their party identification. Except for 120 respondents  who did not respond or picked not sure/don't know, the rest stated the party they identified with.  Of the 1,080 individuals who report party identification, 82 percent lean either Republican or Democrat. The remaining 18 percent identify as independent.

>>>>

In this paper, we investigate how much pornography Americans consume online. Using passive browsing data from YouGov, we find that there is a sharp skew in the consumption of pornography, with a small set of users consuming a large chunk of pornography. About 68 percent of the respondents abstained from consuming pornography online during the month long observation period. Of the people who consumed pornography, the median consumer spent about 44 minutes consuming pornography and the 95th percentile consumer spent 337 minutes.

We also use the data to shed light on an age-old debate---whether Democrats consume more pornography than Republicans or vice versa. Both parties claim the higher moral ground. And in surveys both parties think consumption of pornography is abhorrent. Unlike previous research, which relied on ecological inference, we find that Democrats consume about as much pornography online as Republicans \citep{macinnis2015american, edelman2009markets}. Adjusting for background attributes like age, gender etc., makes little difference.

\section*{Data}\label{sec:data}
We use data from YouGov to measure the consumption of adult content \citep{data-dataverse}. YouGov maintains a large panel that is recruits using various methods. YouGov uses matched sampling to survey respondents: it first draws a random sample from a large synthetic representative sampling frame, finds respondents that match the sampled individuals from its panel, and invites them to take a survey. For data on how well Yougov is able to approximate a random sample, see \citet{rivers2009}. For our sample, panelists also shared de-identified web browsing data tracked via passive metering software installed voluntarily on their computers. The software, called RealityMine, captures online visits independent of the type of browser or browser-specific privacy settings.

The data are from 1,200 respondents and contains a month of data from June, 2022. In all, we have data on about 6 million visits. For each visit, we have information on the domain (e.g., wikipedia.org), the time of visit, and the time spent on the domain. The respondents visited about 64k unique sites, of which 900 are pornographic sites.

Our data also includes characteristics of the 1,200 individuals. We have data on demographic characteristics like birth year, state, gender, race, and education level. We also have information on their party identification. Except for 120 respondents  who did not respond or picked not sure/don't know, the rest stated the party they identified with.  Of the 1,080 individuals who report party identification, 82 percent lean either Republican or Democrat. The remaining 18 percent identify as independent.
